\documentclass[11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{bookmark}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\setlength{\footskip}{5pt}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%== begin commands ==%
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingShort}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%== end commands ==%


%== begin document ==%
\begin{document}

    \begin{center}
        \textbf{\Huge Dylan Petzko} \\ \vspace{1pt}
            \href{mailto:petzkod@gmail.com}{\underline{petzkod@gmail.com}} $|$
            \href{https://linkedin.com/in/dylan-petzko}{\underline{linkedin/dylan-petzko}} $|$
            \href{https://github.com/petzkod5}{\underline{github/petzkod5}}\\
        \vspace{6pt}
    \end{center}

    \section{Education}
        \resumeSubHeadingListStart
            \resumeSubheading
                {Rowan University}{Glassboro, NJ}
                {Bachelor Computing and Informatics, Minor CyberSecurity}{2016 - 2020}
            \resumeSubheading
                {Rowan University}{Glassboro, NJ}
                {Bachelor Emergency Management and Homeland Security, Minor Counter-Terrorism}{2016-2020}
        \resumeSubHeadingListEnd


    \section{Work Experience}
        \resumeSubHeadingListStart
            \resumeSubheadingShort
                {Lockheed Martin, RMS $|$ Mount Laurel, NJ}{Aug 2022 - Current}

                \resumeSubSubheading{Full Stack Engineer II $|$ Cloud}{December 2025 - Current}
                    \resumeItemListStart
                        \resumeItem{
                            Engineered and managed production-grade Kubernetes clusters using Helm.
                            Streamlined the deployment of core services including Keycloak and Kafka
                            across restricted, air-gapped environments.
                        }
                        \resumeItem{
                            Architected a comprehensive monitoring stack using Prometheus, Grafana, and Loki
                            to provide real-time visibility and log aggregation for mission-critical DOD
                            infrastructure.
                        }
                        \resumeItem{
                            Implemented STIG compliance and navigate security compliance requirements to ensure
                            all deployments meet the highest security standards.
                        }
                    \resumeItemListEnd

                \resumeSubSubheading{Software Engineer $|$ DevSecOps}{February 2023 - Current}
                    \resumeItemListStart
                        \resumeItem{
                            Developed inner-source data-analysis python library for proprietary data formats, reducing
                            data-analysis time for users by 75\% and saving over \$750,000 in labor costs per year.
                        }
                        \resumeItem{
                            Created End-To-End CI/CD deployment pipelines using Docker, Vagrant, Splunk, Ansible, and GitLab
                        }
                        \resumeItem{
                            Coordinated efforts between functional products to develop automated deployment tool for container,
                            virtual, and baremetal deployments with estimated cost savings of \$1,000,000 year-over-year.
                        }
                    \resumeItemListEnd

                \resumeSubSubheading{Software Engineer II $|$ Test Automation}{Oct 2023 - December 2025}
                    \resumeItemListStart
                        \resumeItem{
                            Developed and maintained proprietary automated testing framework for end-to-end regression 
                            testing of mission-critical systems using Python, Jenkins, and Gitlab CI/CD. Utilization of this testing
                            framework has estimated cost-savings in development time of over \$500,000 a year.
                        }
                        \resumeItem{
                            Collaborated closely with customer program leadership to drive development priorities and improve
                            product reliability. Created quality and expectation documentation for functional and performance metrics.
                        }
                        \resumeItem{
                            Architected and developed automated testing tools in Python, which helped save \$200,000
                            in development costs year-over-year
                        }
                    \resumeItemListEnd

                \resumeSubSubheading{Systems Engineer $|$ Integration And Test}{Aug 2022 - Oct 2023}
                    \resumeItemListStart
                        \resumeItem{
                            Worked on-site with foreign military customers to troubleshoot and update software builds.
                        }
                        \resumeItem{
                            Coordinate, Develop, and execute detailed test procedures for software products.
                        }
                        \resumeItem{
                            Developed post-test data analysis tool for automated reporting utilizing Python, Matlab and Tableau.
                        }
                        \resumeItem{
                            Developed new, and modified existing software requirement documentation utilizing Jazz and DOORS.
                        }
                    \resumeItemListEnd
            
            \resumeSubheadingShort
                {Stilog I.S.T $|$ NY, NY}{Jan 2021 - Aug 2022}
                \resumeItemListStart
                    \resumeItem{Collaborated with customers to deliver tailored and custom software solutions based on proprietary software framework.}
                    \resumeItem{Utilized Java, HTML, and CSS to meet customer expectations and demands.}
                    \resumeItem{Created comprehensive business requirement documentation to translate customer needs into actionable designable plans.}
                    \resumeItem{Maintained deployment of customer products using Azure and AWS.}
                \resumeItemListEnd
            
            
    \section{Projects}
        \resumeSubHeadingListStart
            \resumeProjectHeading
                {\href{https://petzko.online}{\emph{petzko.online $|$ Personal Website $|$ Python, DockerCompose, NixOS}}}{March 2020 - Dec 2024}
                \resumeItemListStart
                    \resumeItem{
                        Developed personal portfolio website hosted on personal hardware targetting self-healing and high-availability
                    }
                    \resumeItem{
                        Containerized using Dockerfiles and Docker Compose best practices
                    }
                    \resumeItem{
                        Deployed Splunk and Grafana to monitor docker nodes and to fire alerts when certain conditions are met.
                    }
                    \resumeItem{
                        Setup Nginx ingress / egress Routing rules for docker-compose containers
                    }
                \resumeItemListEnd
        \resumeSubHeadingListEnd


    \section{Skills}

        \begin{itemize}[leftmargin=0.15in, label={}]
            \small{\item{
                \textbf{Programming Languages}{: Python, Bash, Go, Groovy/Java, Rust, C++, SQL}\\
                \textbf{OS Platforms}{: UNIX (Solaris 8,9,10), RHEL (6,7,8,9), Ubuntu, Linux 5/6, NixOS}\\
                \textbf{CI Tools}{: Jenkins/Hudson, GitLab, ArgoCD, FluxCD }\\
                \textbf{Configuration Management}{: Ansible, Nix, Nginx, Chef, Puppet, ANT, Maven, Make}\\
                \textbf{Provisioning Tools}{: Terraform, Azure Resource Manager (ARM), Kubernetes, Docker, MiniKube}\\
                \textbf{Virtualization}{: VMWare, Vagrant, KVM}
            }}
        \end{itemize}
                

        \resumeSubHeadingListEnd
\end{document}
%== end document ==%
